---
title: "Approach and Avoidance in Online Dating Experience and Success"
author: "Sue"
output: 
  html_document:
    code_folding: hide
    theme: cosmo
    highlight: tango
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    df_print: paged
    fig_width: 8
    fig_height: 5
  word_document: default
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, highlight = TRUE)
library("tidyverse"); library("corrr"); library("broom"); library("lavaan")
options(digits = 3, scipen = 999)
set.seed(33333)
```

```{r data_import, message = FALSE, include=FALSE}
here::here("data") %>%
  list.files()  %>%
  purrr::map(function(file_name) {
    assign(x = str_remove(file_name, "_anonymized_processed_data.csv"),
           value = readr::read_csv(paste(here::here("data"), sep = "/", file_name)),
           envir = .GlobalEnv)
  })
```


```{r message = FALSE, include = FALSE}
list.files(path = here::here("r-scripts"),
           pattern = "*.R",
           full.names = T) %>%
  purrr::map(~source(.)) 
```

```{r data_cleaning}
# participant exclusion criteria
# study 2
s2a <- s2a %>%
  mutate(exclusion = case_when(
    attn_check == "pass" &
      var_low == "acceptable" &
      duplicate == "nonduplicated" ~ "eligible",
    TRUE ~ "ineligible"))
# study 3
s2b <- s2b %>%
  mutate(exclusion = case_when(
    attn_check == "pass" ~ "eligible",
    TRUE ~ "ineligible"))
# study 4
s3 <- s3 %>%
  mutate(exclusion = case_when(
    attn_check == "pass" &
      duplicate == "nonduplicated" ~ "eligible",
    TRUE ~ "ineligible"))

# follow-up study
# making column names in S4 consistent with the other datasets
s4 <- s4 %>% 
  rename(fit_ease = "ease",
         fit_engage = "engagement",
         fit_success = "ods") %>% 
  mutate(gender = recode_factor(gender, 
                                man = "male", woman = "female", nonbinary = "nonbinary", 
                                .missing = "other")) 
```

```{r}
# creating an aggregate score for all 3 bas subscales
s4 <- s4 %>% 
  mutate(bas = s4 %>% 
           select(starts_with("bas"), -bas_reward, -bas_drive, -bas_fun) %>% 
           # psych::alpha(check.keys = T)
           rowMeans(na.rm = T))
```

```{r data_scoring}
# scoring key variables: engage, ease, success_strategy, ods
source(here::here("data_analysis", "data_prep", "item_scoring.R"))
```


# Method  
## Participants  
```{r sample_size}
n_1to4 <- list(s1, s2a, s2b, s3, s4) %>% 
  map(count, exclusion) %>% 
  map_dfr(filter, exclusion == "eligible", .id = "study") %>% 
  pull(n)
```

```{r}
list(s1, s2a, s2b, s3, s4) %>% 
  map_dfr(count, exclusion, .id = "study") %>% 
  spread(exclusion, n) %>% 
  mutate(exclusion_rate = (ineligible/(eligible+ineligible))*100)
```


```{r demo_age}
list(s1, s2a, s2b, s3, s4) %>% 
  map_dfr(demo_age, .id = "study") %>% 
  filter(exclusion == "eligible") 
  
```

```{r demo_gender}
list(s1, s2a, s2b, s3, s4) %>% 
  map_dfr(count, exclusion, gender, .id = "study") %>% 
  spread(gender, n) %>% 
  filter(exclusion == "eligible") %>% 
  mutate(prop_female = (female / (female + male)*100))
```


```{r demo_ethnicity}
list(s1, s2a, s2b, s3, s4) %>% 
  map(ethnicity)
```


## Measures  

### RFQ in relationships
Prevention focus
```{r}
list(s1, s2a, s2b, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^RFQ_M_[1-7]")) %>% # prevention items
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study")
```

Promotion focus
```{r}
list(s1, s2a, s2b, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, paste("RFQ_M", 8:15, sep = "_")) %>% # promotion items
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study")
```
### BIS/BAS
BIS
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(matches("^bis_[0-9]")) %>% # bis-items
  psych::alpha(check.keys = TRUE)
```
BAS
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(matches("^bas\\w_")) %>% # bas items
  psych::alpha(check.keys = TRUE)
```

#### r(social motives)
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(promotion, bas, rfq_prom, prevention, bis, rfq_prev) %>% 
  corrr::correlate()
```
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(promotion, bas) %>% 
  cor.test(~promotion + bas, data = .)
```

```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(prevention, bis) %>% 
  cor.test(~prevention + bis, data = .)
```


### Online Dating
#### Engagement & Ease
Engagement
s2a: "overall_engagement"; s2b-s4: "engage"

```{r}
list(s2a, s2b, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^engage_[1-3]")| matches("^overall_engagement_[1-3]")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study")
```
Ease 
```{r}
list(s2a, s2b, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^ease_[1-2|4]")| matches("^overall_ease_[1|3|5]")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study")
```
#### Success
```{r}
list(s1, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^suc_[0-9]{1,2}")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study")
```




### approach
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  select(promotion, rfq_prom,  bas) %>% 
  corrr::correlate()
```
GRFQ correlated with bas, $r$ = .41.
Higgins' RFQ correlated with BAS, $r$ = .27. 

### avoidance
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  select(prevention, rfq_prev, bis) %>% 
  corrr::correlate()
```
GRFQ correlated with bis, $r$ = .47.
Higgins' RFQ correlated with BAS, $r$ = -0.09. 


# Result  
## Meta analysis  
```{r}
library("metafor")
```


```{r regression_meta}
# regressing RFQ (promotion and prevention) on y 
regression_meta <- function(df, y) {
  lmfit <- df %>% 
    filter(exclusion == "eligible") %>% # excluding ineligible participants
    centre_pred(var = c("promotion", "prevention")) %>% # centring predictors
    lm(eval(rlang::sym(y)) ~ promotion.c + prevention.c, # fit regression
       data = .)
  list(r2 = broom::glance(lmfit)$r.squared, # regression model R2
       promotion_t = broom::tidy(lmfit)$statistic[2], # t-value 
       prevention_t = broom::tidy(lmfit)$statistic[3],
       promotion_b = broom::tidy(lmfit)$estimate[2], # estimate
       prevention_b = broom::tidy(lmfit)$estimate[3],
       promotion_se = broom::tidy(lmfit)$std.error[2], # std. error
       prevention_se = broom::tidy(lmfit)$std.error[3],
       promotion_p = broom::tidy(lmfit)$p.value[2], # p-value
       prevention_p = broom::tidy(lmfit)$p.value[3]) 
}
```

### Online dating experience
#### Engagement  




```{r engage_meta}
# predictor: `engagement` with the same items across studies  
engage_meta <- list(s2a, s2b, s3, s4) %>% 
   map_dfr(regression_meta, y = "engage", .id = "study_id") %>% 
   mutate(ni = n_1to4[-1])
```
```{r}
engage_prom_spcor = metafor::escalc(data = engage_meta,
                measure = "SPCOR", # semi-partial correlation
                ti = promotion_t, # t-value of promotion.c
                r2i = r2,
                ni =  ni,
                mi = rep(3, 4),
                digits = 2)
```

```{r}
engage_prev_spcor = metafor::escalc(data = engage_meta,
                measure = "SPCOR", # semi-partial correlation
                ti = prevention_t, # t-value of promotion.c
                r2i = r2,
                ni =  ni,
                mi = rep(3, 4),
                digits = 2)
```


##### Promotion

```{r engage_promotion, cache=TRUE}
(engage_promotion <- list("FE", "REML") %>% 
  map(~rma(data = engage_meta,
          method = ., # restricted maximum-likelihood estimator
          measure = "SPCOR", # semi-partial correlation
          ti = promotion_t, # t-value of promotion.c
          r2i = r2,
          ni =  ni,
          mi = rep(3, 4), # number of predictors
          slab = paste0(study_id, " [N = ", ni, "]"))))

# engage_promotion <- engage_meta %>%
#    rma(method = "REML", # restricted maximum-likelihood estimator
#        measure = "SPCOR", # semi-partial correlation
#        ti = .$promotion_t, # t-value of promotion.c
#        r2i = .$r2,
#        ni =  .$ni,
#        mi = rep(3, 4), # number of predictors
#        data = .,
#        slab = paste0(study_id, " [N = ", ni, "]"))
```


```{r}
metafor::forest.rma(engage_promotion[[1]], # fixed effect
                    annotate = TRUE, addcred = TRUE)
```

##### Prevention
```{r engage_prevention, cache = TRUE}

(engage_prevention <- list("FE", "REML") %>% 
  map(~rma(data = engage_meta,
          method = ., # restricted maximum-likelihood estimator
          measure = "SPCOR", # semi-partial correlation
          ti = prevention_t, # t-value of promotion.c
          r2i = r2,
          ni =  ni,
          mi = rep(3, 4), # number of predictors
          slab = paste0(study_id, " [N = ", ni, "]"))))

# engage_prevention <- engage_meta %>% 
#   rma(method = "REML", 
#       measure = "SPCOR", 
#       ti = .$prevention_t, # t-value of prevention.c
#       r2i = .$r2,
#       ni =  .$ni,
#       mi = rep(3, 4),
#       data = .,
#       slab = paste0(study_id, " [N = ", ni, "]"))
```

```{r}
metafor::forest.rma(engage_prevention[[1]], # fixed effect
                    annotate = TRUE, addcred = TRUE)
```


#### Ease     
```{r ease_meta}
(ease_meta <- list(s2a, s2b, s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map_dfr(regression_meta, y = "ease", .id = "study_id") %>% 
   mutate(ni = n_1to4[-1]))
```
```{r}
ease_prev_spcor = metafor::escalc(data = ease_meta,
                 measure = "SPCOR", # semi-partial correlation
                 ti = prevention_t, # t-value of promotion.c
                 r2i = r2,
                 ni =  ni,
                 mi = rep(3, 4),
                 digits = 2)
```

```{r}
ease_prom_spcor = metafor::escalc(data = ease_meta,
                 measure = "SPCOR", # semi-partial correlation
                 ti = promotion_t, # t-value of promotion.c
                 r2i = r2,
                 ni =  ni,
                 mi = rep(3, 4),
                 digits = 2)
```


##### Prevention

```{r ease_prevention, cache = TRUE}
(ease_prevention <- list("FE", "REML") %>% 
  map(~rma(data = ease_meta,
          method = ., # restricted maximum-likelihood estimator
          measure = "SPCOR", # semi-partial correlation
          ti = prevention_t, # t-value of promotion.c
          r2i = r2,
          ni =  ni,
          mi = rep(3, 4), # number of predictors
          slab = paste0(study_id, " [N = ", ni, "]"))))
```



```{r}
metafor::forest.rma(ease_prevention[[2]], # REML model
                    annotate = TRUE, addcred = TRUE)
```

##### Promotion
```{r ease_promotion, cache = TRUE}
(ease_promotion <- list("FE", "REML") %>% 
  map(~rma(data = ease_meta,
           method = ., 
           measure = "SPCOR", 
           ti = promotion_t, # t-value of promotion.c
           r2i = r2,
           ni =  ni,
           mi = rep(3, 4),
           slab = paste0(study_id, " [N = ", ni, "]"))))
```

```{r}
metafor::forest.rma(ease_promotion[[2]], annotate = TRUE, addcred = TRUE)
```


### Online dating success  


```{r success_meta}
success_meta <- list(s1, s3, s4) %>% 
  map_dfr(regression_meta, y = "ods", .id = "study_id") %>% 
   mutate(ni = c(220, 480, 150),
          study_id = c("s1", "s3", "s4"))
```


```{r}
success_spcor = metafor::escalc(data = success_meta,
                  measure = "SPCOR", # semi-partial correlation
                  ti = promotion_t, # t-value of promotion.c
                  r2i = r2,
                  ni =  ni,
                  mi = rep(3, 3),
                  digits = 2)

success_prev_spcor = metafor::escalc(data = success_meta,
                  measure = "SPCOR", # semi-partial correlation
                  ti = prevention_t, # t-value of promotion.c
                  r2i = r2,
                  ni =  ni,
                  mi = rep(3, 3),
                  digits = 2)

```


```{r ods_effect_size}
(success_meta %>% 
  pivot_longer(.,
    cols = promotion_t:prevention_p,
               names_to = c("rfq", ".value"),
               names_pattern = "(.*)_(.*)"))
```


#### Promotion
```{r success_promotion, cache = TRUE}
# (success_promotion <- 
(success_promotion <- list("FE", "REML") %>%    
  map(~rma(data = success_meta,
           method = .,
           measure = "SPCOR", 
           ti = promotion_t, # t-value of promotion.c
           r2i = r2,
           ni =  ni,
           mi = rep(3, 3),
           slab = paste0(study_id, " [N = ", ni, "]"))))
```


```{r}
metafor::forest.rma(success_promotion[[1]], # fixed effect
                    annotate = TRUE, addcred = TRUE)
```

#### Prevention
```{r success_prevention, cache = TRUE}

(success_prevention <- list("FE", "REML") %>%    
  map(~rma(data = success_meta,
           method = .,
           measure = "SPCOR", 
           ti = prevention_t, # t-value of promotion.c
           r2i = r2,
           ni =  ni,
           mi = rep(3, 3),
           slab = paste0(study_id, " [N = ", ni, "]"))))


# (success_prevention <- success_meta %>% 
#   rma(method = "REML", 
#       measure = "SPCOR", 
#       ti = .$prevention_t, # t-value of prevention.c
#       r2i = .$r2,
#       ni =  .$ni,
#       mi = rep(3, 3),
#       data = .,
#       slab = paste0(study_id, " [N = ", ni, "]")))
```



```{r}
metafor::forest.rma(success_prevention[[1]], # fixed effect
                    annotate = TRUE, addcred = TRUE)
```

## Social motive regression
### Online Dating Experience
```{r}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas", 
                      "rfq_prom", "rfq_prev")) %>% 
  lm(cbind(engage, ease) ~ promotion.c + prevention.c + bis.c + bas.c,
     data = .) %>% 
  broom::tidy() %>% 
  mutate_at("p.value", round, 3)
  # car::Anova(3) %>% 
  # summary
```


#### Engagement
```{r engage_regression}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas", 
                      "rfq_prom", "rfq_prev")) %>% 
  lm(engage ~ promotion.c + prevention.c + bis.c + bas.c,
     data = .) %>% 
  # glance()
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r egnage_bisbas}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("bis", "bas")) %>% 
  lm(engage ~ bis.c + bas.c, 
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r engage_higgins}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("rfq_prom", "rfq_prev")) %>% 
  lm(engage ~ rfq_prom.c + rfq_prev.c, 
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

#### Ease
```{r ease_regression}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas", 
                      "rfq_prom", "rfq_prev")) %>% 
  lm(ease ~ promotion.c + prevention.c + bis.c + bas.c + rfq_prom.c + rfq_prev.c,
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r ease_general}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention")) %>% 
  lm(ease ~ promotion.c + prevention.c,
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r ease_higgins}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("rfq_prom", "rfq_prev")) %>% 
  lm(ease ~ rfq_prom.c + rfq_prev.c, 
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r ease_bisbas}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("bis", "bas")) %>% 
  lm(ease ~ bis.c + bas.c, 
     data = .) %>% 
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

### Success

```{r ods_regression}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas")) %>% 
  lm(ods ~ promotion.c + prevention.c + bis.c + bas.c ,
     data = .) %>% 
  # sjPlot::tab_model(show.stat = TRUE, show.std = "std", string.stat = "\bt",
  #                   dv.labels = "Online Dating Success")
  # glance()
  tidy() %>% 
  mutate_at("p.value", round, 3)
```

```{r ods_rfq}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention")) %>% 
  lm(ods ~ promotion.c + prevention.c , 
     data = .) %>% 
  # broom::glance()
  broom::tidy() %>%
  mutate_at("p.value", round, 3)
  car::Anova(type = 3) %>% 
  effectsize::effectsize()
```


```{r ods_bisbas}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("bis", "bas")) %>% 
  lm(ods ~ bis.c + bas.c, 
     data = .) %>% 
  broom::tidy() %>% 
  mutate_at("p.value", round, 3)
  broom::glance()
```


```{r ods_higgins}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  lm(ods ~ rfq_prom + rfq_prev, 
     data = .) %>% 
  summary()
```

```{r success-regression-table}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas")) %>% 
  lm(ods ~ promotion.c + prevention.c + bis.c + bas.c ,
     data = .) %>% 
  sjPlot::tab_model(show.stat = TRUE, show.se = TRUE, show.std = "std", string.stat = "\bt",
                    dv.labels = "Online Dating Success", file = "success_reg_table.html")
```


## Mediation analysis  

### Strategy-specific success
```{r}
library("OpenMx");library("metaSEM")
```

#### Promotion 
```{r promotion_mediation, cache = TRUE, eval=error_fixed}
# strategy-specific success & RFQ mediated through engage & ease
promotion_mediation <- list(s2a, s2b, s3) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, promotion, engage, ease, success_strategy) %>% 
  map(cor, use = "pairwise.complete.obs") %>% 
  tssem1(.,
         n = c(200, 300, 480),
         method = "REM")
```

```{r eval=error_fixed}
summary(promotion_mediation)
```

```{r eval=error_fixed}
coef(promotion_mediation)
```



```{r eval=error_fixed}
A_prom <- matrix(c(0, 0, 0, 0,
                   "0.2*prom_engage", 0            , 0            , 0,
                   "0.2*prom_ease", 0, 0            , 0,
                   "0.2*prom_success", "0.2*engage_success", "0.2*ease_success", 0),
                 ncol = 4, nrow=4, byrow=TRUE)
dimnames(A_prom)[[1]] <- dimnames(A_prom)[[2]] <- c("prom", "engage", "ease", "success")
A_prom <- as.mxMatrix(A_prom)
```

```{r eval=error_fixed}
# S_prom <- Diag(c(1, "0.1*eEngage", "0.1*eEase", "0.1*eSuccess"))
S_prom <- matrix(c("0.1*eProm", 0, 0, 0,
                   0, "0.1*eEngage", "0.1*eEngageEase", 0,
                   0, "0.1*eEngageEase", "0.1*eEase", 0,
                   0, 0, 0, "0.1*eSuccess"),
                 ncol = 4, byrow = T)
dimnames(S_prom)[[1]] <- dimnames(S_prom)[[2]] <- c("prom", "engage", "ease", "success")
S_prom <- as.mxMatrix(S_prom)
```

```{r eval=error_fixed}
prom_mediation_model <- tssem2(promotion_mediation,
       Amatrix = A_prom,
       Smatrix = S_prom,
       intervals.type = "LB",
       diag.constraints = TRUE,
       mx.algebras = list(totalEffect = mxAlgebra(prom_engage*engage_success +
                                                       prom_ease*ease_success +
                                                       prom_success,
                                                     name = "totalEffect"), 
                          totalIndirect = mxAlgebra(prom_engage*engage_success + 
                                                      prom_ease*ease_success,
                                                    name = "totalIndirect"),
                          indirect_engage = mxAlgebra(prom_engage*engage_success,
                                                      name = "indirect_engage"),
                          indirect_ease = mxAlgebra(prom_ease*ease_success,
                                                    name = "indirect_ease")))
```

```{r eval=error_fixed}
summary(prom_mediation_model)
# prom_mediation_model <- rerun(prom_mediation_model)
```


```{r prom_mediation_plot, eval=error_fixed}

meta2semPlot(prom_mediation_model) %>% 
  semPlot::semPaths(whatLabels = "std",
                    layout = matrix(c(-4, 0, # mediator
                                      0, 0.5, # X
                                      0, -0.5,
                                      4, 0),
                                    ncol = 2,
                                    byrow = T),
                    # rotation = 2,
                    sizeMan = 10,
                    sizeLat = 12,
                    curvePivot = TRUE,
                    nodeLabels = c("Promotion\nFocus", "Engagement", "Ease", "Strategy\nSuccess"))
```

#### Prevention

```{r eval=error_fixed}
A_prev <- matrix(c(0, 0, 0,
                   "0.2*prev_ease", 0, 0,
                   "0.2*prev_success", "0.2*ease_success", 0),
                 ncol = 3, nrow = 3, byrow = TRUE)

dimnames(A_prev)[[1]] <- dimnames(A_prev)[[2]] <- c("prev", "ease", "success")
A_prev <- as.mxMatrix(A_prev)
```

```{r eval=error_fixed}
S_prev <- Diag(c(1, "0.1*eEase", "0.1*eSuccess"))
dimnames(S_prev)[[1]] <- dimnames(S_prev)[[2]] <- c("prev", "ease", "success")
S_prev <- as.mxMatrix(S_prev)
```


```{r prevention_mediation, cache = TRUE, eval=error_fixed}
prevention_mediation <- list(s2a, s2b, s3) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, prevention, ease, fit_success) %>% 
  map(cor, use = "pairwise.complete.obs") %>% 
  tssem1(.,
         n = c(200, 300, 480),
         method = "REM") %>% 
  tssem2(.,
         Amatrix = A_prev,
         Smatrix = S_prev,
         intervals.type = "LB",
         diag.constraints = TRUE,
         mx.algebras = list(indirectEffect = mxAlgebra(prev_ease*ease_success,
                                                       name = "indirectEffect"),
                            totalEffect = mxAlgebra(prev_ease*ease_success + 
                                                      prev_success,
                                                    name = "totalEffect")))
```


```{r eval=error_fixed}
summary(prevention_mediation)
```

```{r eval=error_fixed}
meta2semPlot(prevention_mediation) %>% 
  semPlot::semPaths(whatLabels = "est",
                    layout = matrix(c(-4, 0, # mediator
                                      0, 0.5, # X
                                      4, 0),
                                    ncol = 2,
                                    byrow = T),
                    sizeMan = 10,
                    nodeLabels = c("Prevention\nFocus", "Ease", "Online Dating\nSuccess"))
```


### General success
#### Promotion focus
```{r eval=error_fixed}
prom_ods_A <- matrix(c(0, 0, 0, 0,
                       "0.2*prom_engage", 0            , 0            , 0,
                       "0.2*prom_ease", 0, 0            , 0,
                       "0.2*prom_success", "0.2*engage_success", "0.2*ease_success", 0),
                     ncol = 4, nrow=4, byrow=TRUE)
dimnames(prom_ods_A)[[1]] <- dimnames(prom_ods_A)[[2]] <- c("prom", "engage", "ease", "success")
prom_ods_A  <- as.mxMatrix(prom_ods_A)
```


```{r eval=error_fixed}
prom_ods_S <- matrix(c(1, 0, 0, 0,
                       0, "0.1*eEngage", "0.1*eEngageEase", 0,
                       0, "0.1*eEngageEase", "0.1*eEase", 0,
                       0, 0, 0, "0.1*eSuccess"),
                     ncol = 4, byrow = T)

dimnames(prom_ods_S)[[1]] <- dimnames(prom_ods_S)[[2]] <- c("prom", "engage", "ease", "success")
prom_ods_S <- as.mxMatrix(prom_ods_S)
```

```{r promotion_ods_mediation, cache = TRUE, eval=error_fixed}
# strategy-specific success & RFQ mediated through engage & ease
promotion_ods_mediation <- list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, promotion, engage, ease, ods) %>% 
  map(cor, use = "pairwise.complete.obs") %>% 
  tssem1(.,
         n = c(480, 150),
         method = "REM") %>% 
  tssem2(.,
         Amatrix = prom_ods_A,
         Smatrix = prom_ods_S,
         intervals.type = "LB",
         diag.constraints = TRUE,
         mx.algebras = list(totalEffect = mxAlgebra(prom_engage*engage_success +
                                                      prom_ease*ease_success +
                                                      prom_success,
                                                    name = "totalEffect"), 
                            totalIndirect = mxAlgebra(prom_engage*engage_success + 
                                                        prom_ease*ease_success,
                                                      name = "totalIndirect"),
                            indirect_engage = mxAlgebra(prom_engage*engage_success,
                                                        name = "indirect_engage"),
                            indirect_ease = mxAlgebra(prom_ease*ease_success,
                                                      name = "indirect_ease")))
```

```{r eval=error_fixed}
summary(promotion_ods_mediation)
```

```{r prom_ods_mediation_plot, eval=error_fixed}
meta2semPlot(promotion_ods_mediation) %>% 
  semPlot::semPaths(whatLabels = "std",
                    layout = matrix(c(-4, 0, # mediator
                                      0, 0.5, # X
                                      0, -0.5,
                                      4, 0),
                                    ncol = 2,
                                    byrow = T),
                    # rotation = 2,
                    sizeMan = 10,
                    sizeLat = 12,
                    curvePivot = TRUE,
                    nodeLabels = c("Promotion\nFocus", "Engagement", "Ease", "Strategy\nSuccess"))
```




#### Prevention 
```{r eval=error_fixed}
prev_ods_A <- matrix(c(0, 0, 0,
                   "0.2*prev_ease", 0, 0,
                   "0.2*prev_success", "0.2*ease_success", 0),
                 ncol = 3, nrow = 3, byrow = TRUE)

dimnames(prev_ods_A)[[1]] <- dimnames(prev_ods_A)[[2]] <- c("prev", "ease", "success")
prev_ods_A <- as.mxMatrix(prev_ods_A)
```

```{r eval=error_fixed}
prev_ods_S <- Diag(c(1, "0.1*eEase", "0.1*eSuccess"))
dimnames(prev_ods_S)[[1]] <- dimnames(prev_ods_S)[[2]] <- c("prev", "ease", "success")
prev_ods_S <- as.mxMatrix(prev_ods_S)
```


```{r prevention_ods_mediation, cache = TRUE, eval=error_fixed}
prevention_ods_mediation <- list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, prevention, ease, ods) %>% 
  map(cor, use = "pairwise.complete.obs") %>% 
  tssem1(.,
         n = c(480, 150),
         method = "REM") %>% 
  tssem2(.,
         Amatrix = prev_ods_A,
         Smatrix = prev_ods_S,
         intervals.type = "LB",
         diag.constraints = TRUE,
         mx.algebras = list(indirectEffect = mxAlgebra(prev_ease*ease_success,
                                                       name = "indirectEffect"),
                            totalEffect = mxAlgebra(prev_ease*ease_success + 
                                                      prev_success,
                                                    name = "totalEffect")))
```

```{r eval=error_fixed}
summary(prevention_ods_mediation)
```


```{r prevention_ods_model}
prevention_ods_model <- '
  # regressions
  ods ~ b1*ease + c1*prevention

  ease ~ a1*prevention

  # indirect paths
  ease_indirect := a1 * b1
  
  # total
  total := c1 + (a1 * b1)
'
```


```{r prev_sem_parameter}
list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(~mutate_at(., vars(c("ease", "prevention")), mean_x)) %>% 
  map(~sem(prevention_ods_model, 
           data = .x)) %>% 
  #map(summary, fit.measures = TRUE, standardized = TRUE) %>% 
  map_dfr(tidy, .id = "study") %>% 
  # select(study, term, label, std.all, std.error, conf.low, conf.high, statistic, p.value) %>% 
  # filter(label == "ease_indirect") %>% 
  filter(label %in% c("a1", "a2", "b1", "b2", "c1", "engage_indirect", "ease_indirect", "total_indirect", "total")) %>%
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::select(study, label, std.all, std.error, statistic, p.value) 
```

```{r}
s3 %>% 
  filter(exclusion == "eligible") %>% 
  mutate_at(vars(c("ease", "prevention")), mean_x) %>% 
  sem(prevention_ods_model, data = .) %>% 
  summary(fit.measures = TRUE, standardized = TRUE)
```


### Confirmatory Mediation Analysis (S4)
```{r mediation_packages}
library("mediation")
source("/Users/suesong/R/r-scripts/mediations_patch.r")
```

#### Promotion
```{r eval=FALSE}
# error not fixed
prom_mediation <- function(df) {
  prom_data = df %>% 
    centre_pred(var = c("promotion", "engage", "ease")) %>% 
    dplyr::select(promotion.c, engage.c, ease.c, ods) %>% 
    list(dataset = .)
  
  mediation.result <- mediations(prom_data,
                                 "promotion.c", # X
                                 c("engage.c", "ease.c"), # mediators
                                 "ods", # Y
                                 boot = TRUE,
                                 sims = 5000)
  mediation.summary <- augment_summary(mediation.result)
  med.res <- list(mediation.summary, standard_errors(mediation.result))
  
  return(med.res)
}

s4 %>% 
  filter(exclusion == "eligible") %>% 
  prom_mediation
```


```{r}
# engagement only without ease as a mediator
prom_mediation <- function(df) {
  a_path <- df %>%
    lm(engage ~ promotion,
       data = .)
  
  b_path <- df %>%
    lm(ods ~ promotion + engage,
       data = .)
  
  mediation.result <- mediate(a_path,
                              b_path,
                              treat = "promotion",
                              mediator = "engage",
                              boot = TRUE,
                              sims = 5000)
  mediation.summary <- summary(mediation.result)
  med.res <- list(mediation.summary, standard_errors(mediation.result))
  
  return(med.res)
}

list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(mutate_at, "engage", mean_x) %>% 
  map(prom_mediation)
```




```{r promotion_ods_model}
promotion_ods_model <- '
  # regressions
  ods ~ b1*engage + b2*ease + c1*promotion

  engage ~ a1*promotion 
  ease ~ a2*promotion
  
  engage ~~ ease

  # indirect paths
  engage_indirect := a1 * b1
  ease_indirect := a2 * b2
  
  total_indirect := (a1 * b1) + (a2 * b2)
  
  # total
  total := c1 + (a1 * b1) + (a2 * b2)
'
```

```{r prom_sem_parameters}
list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(~mutate_at(., vars(c("engage", "ease", "promotion")), mean_x)) %>% 
  map(~sem(promotion_ods_model, 
           data = .x)) %>% 
  # map(summary, fit.measures = TRUE, standardized = TRUE) %>% 
  map_dfr(tidy, .id = "study") %>% 
  # select(study, term, label, std.all, std.error, conf.low, conf.high, statistic, p.value) %>% 
  filter(label %in% c("engage_indirect", "ease_indirect", "total_indirect", "total", "c1")) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  dplyr::select(study, term, label, std.all, std.error, p.value)
```

```{r}
s3 %>% 
  filter(exclusion == "eligible") %>% 
  mutate_at(vars(c("engage", "ease", "promotion")), mean_x) %>% 
  sem(promotion_ods_model, data = .) %>% 
  summary(fit.measures = TRUE, standardized = TRUE)
```



#### Prevention
```{r prev_mediation}
prev_mediation <- function(df) {
  a_path <- df %>%
    lm(ease ~ prevention,
       data = .)
  
  b_path <- df %>%
    lm(ods ~ prevention + ease,
       data = .)
  
  mediation.result <- mediate(a_path,
                              b_path,
                              treat = "prevention",
                              mediator = "ease",
                              boot = TRUE,
                              sims = 5000)
  mediation.summary <- summary(mediation.result)
  med.res <- list(mediation.summary, standard_errors(mediation.result))
  
  return(med.res)
}

s4 %>% 
  filter(exclusion == "eligible") %>% 
  mutate_at(vars(c("ease", "prevention")), mean_x) %>% 
  prev_mediation
```

```{r}
s3 %>% 
  filter(exclusion == "eligible") %>% 
  mutate_at(vars(c("ease", "prevention")), mean_x) %>% 
  prev_mediation
```

## Exploratory Analyses

```{r}
list(s3, s4) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(~lm(ods ~ prevention + promotion + ease + engage,
          data = .)) %>% 
  map_dfr(broom::tidy, .id = "Study") %>% 
  mutate_at("p.value", round, 3) %>% 
  filter(term != "(Intercept)") %>% 
  arrange(term, Study)
```

When entered simultaneously, engagement in profile-browsing predicts subjective success and washes out the effects of promotion and prevention focus. 

