---
title: "Frustrated or Engaged? Regulatory Focus Predicts Experiences with Online Dating"
output:
  word_document:
    reference_docx: apa-styles.docx
    df_print: kable
  bookdown::html_document2:
    code_folding: hide
    theme: cosmo
    highlight: tango
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
    df_print: paged
    fig_width: 8
    fig_height: 5
  html_document:
    toc: yes
    df_print: paged
  bibliography: r-references.bib
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE, highlight = TRUE)
library("tidyverse"); library("corrr"); library("broom"); library("lavaan"); library("bookdown"); library("metafor")
options(digits = 3, scipen = 999)
set.seed(33333)

# If rendering the document as html, change the following to TRUE
render_html = FALSE
# render_html = TRUE
```

```{r data_import, message = FALSE, include=FALSE}
here::here("data") %>%
  list.files()  %>%
  purrr::map(function(file_name) {
    assign(x = str_remove(file_name, "_anonymized_processed_data.csv"),
           value = readr::read_csv(paste(here::here("data"), sep = "/", file_name)),
           envir = .GlobalEnv)
  })
```

```{r message = FALSE, include = FALSE}
list.files(path = here::here("r-scripts"),
           pattern = "*.R",
           full.names = T) %>%
  purrr::map(~source(.)) 
```

```{r}
# correcting miscoded values in S4 
# online dating success responses were erroneously assigned 11 ~ 17 instead of 1 to 7.
s4 = s4 %>% 
  mutate_at(vars(matches("suc_[0-9]")), ~{.x - 10})
```

# Studies 1 - 4: Meta-Analysis
## Method
### Participants
```{r sample_size, include = render_html}
n_1to5 <- objects(pattern = "^s[1-5]$") %>% 
  mget(envir = .GlobalEnv) %>% 
  map(count, exclusion) %>% 
  map_dfr(filter, exclusion == "eligible", .id = "study") %>% 
  pull(n)
```

```{r exclusion_rate, include = render_html}
(exclusion_rate = list(s1, s2, s3, s4, s5) %>% 
   map(filter, Finished == 1) %>% # finished responses
  map_dfr(count, exclusion, .id = "Study") %>% 
  spread(exclusion, n) %>% 
  mutate(exclusion_rate = (ineligible/(eligible+ineligible))*100))
```
The exclusion rates across the five studies, ranging from `r min(exclusion_rate$exclusion_rate)`% to `r max(exclusion_rate$exclusion_rate)`%, are within the expected range reported by previous research on online studies (Goodman et al., 2012). 

```{r demo_gender, include = render_html}
(demo_gender = objects(pattern = "^s[1-5]", envir = .GlobalEnv) %>% 
   mget(envir = .GlobalEnv) %>% 
   # list(s1, s2, s3, s4, s5) %>% 
   map( filter, exclusion == "eligible") %>% 
  map_dfr(count, exclusion, gender, name = "prop", .id = "Study") %>% 
   group_by(Study) %>% 
 mutate(gender_prop = glue::glue("{ round((prop/sum(prop, na.rm = T))*100, 2) }% {gender}"),
        gender_prop = paste0(gender_prop, collapse = "; ")) %>% 
   slice(1) %>% 
   ungroup() %>% 
   select(Study, gender_prop))
```

```{r demo_ethnicity, include = render_html}
(demo_ethnicity = objects(pattern = "^s[1-5]", envir = .GlobalEnv) %>% 
   mget(envir = .GlobalEnv) %>% 
   # list(s1, s2, s3, s4, s5) %>% 
  map_dfr(ethnicity, .id = "Study") %>% 
   mutate(ethnicity = case_when(ethnicity == "ethnicity_1" ~ "Caucasian", 
                                ethnicity == "ethnicity_2" ~ "African Descent", 
                                ethnicity == "ethnicity_3" ~ "South American", 
                                ethnicity == "ethnicity_4" ~ "Middle Eastern",
                                ethnicity == "ethnicity_5" ~ "South Asian", 
                                ethnicity == "ethnicity_6" ~ "Southeast Asian", 
                                ethnicity == "ethnicity_7" ~ "East Asian",
                                ethnicity == "ethnicity_8" ~ "First Nations",
                                ethnicity == "ethnicity_9" ~ "Pacific Islander",
                                TRUE ~ "other")) %>% 
   group_by(Study) %>% 
 mutate(ethnicity_prop = paste0(glue::glue("{ cum_perc } {ethnicity}"), collapse = "; ")) %>% 
   slice(1) %>% 
   ungroup() %>% 
  # filter(ethnicity == "ethnicity_1") %>% 
   dplyr::select(Study, ethnicity_prop)) # caucasian
```
```{r demo_age}
(demo_age = objects(pattern = "^s[1-5]", envir = .GlobalEnv) %>% 
   mget(envir = .GlobalEnv) %>% 
   map_dfr(age, .id = "Study") %>% 
   group_by(Study) %>% 
   mutate(n = glue::glue("{sum(n)} [{n}]")) %>% 
   ungroup() %>% 
   filter(exclusion == "eligible") %>% 
   mutate_if(is.double, round) %>% 
  mutate(mean_age = glue::glue("$M$ = {age.m} ({age.min} - {age.max})")) %>% 
   select(Study, n, mean_age))
  # mutate(`N [eligible]` = str_c((ineligible+eligible), " [",eligible,"]"), .after = Study, .keep = "unused")
   
```
Study characteristics (e.g., measures used) and participant demographics are summarized in Table \@ref(tab:study-information).
```{r study-information}
study_info = objects(pattern = "^demo_", envir = .GlobalEnv) %>% 
   mget(envir = .GlobalEnv) %>% 
   reduce(full_join, by = "Study")

knitr::kable(study_info, caption = "Study Information and Sample Demographics for Studies")
  # mutate(`N [eligible]` = str_c((ineligible+eligible), " [",eligible,"]"), .after = Study, .keep = "unused"))
```

  
### Measures  
#### Regulatory Focus in Relationship Scale   

```{r include = render_html}
(prevention_alpha = paste0("s", c(1:5)) %>% 
  # list(s1, s2, s3, s4, s5) %>% 
       mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^RFQ_M_[1-7]")) %>% # prevention items
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study"))
```

Prevention focus ($a$ = `r paste(round(prevention_alpha$raw_alpha, 2), sep = ", ")`)

```{r include = render_html}
(promotion_alpha = paste0("s", c(1:5)) %>% 
  # list(s1, s2, s3, s4, s5) %>% 
       mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, paste("RFQ_M", 8:15, sep = "_")) %>% # promotion items
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study"))
```

Promotion focus ($a$ = `r paste(round(promotion_alpha$raw_alpha, 2), sep = ", ")`)

#### Online Dating Success   
```{r include = render_html}
(success_alpha = paste0("s", c(1, 4, 5)) %>% 
  # list(s1, s4, s5) %>% 
       mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^suc_[0-9]{1,2}")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study"))
```

Online dating success ($a$ = `r paste(round(success_alpha$raw_alpha, 2), sep = ", ")`)

#### Engagement and Ease   
```{r include = render_html}
(engagement_alpha = paste0("s", c(2:5)) %>% 
  # list(s2, s3, s4, s5) %>% 
       mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^engage_[1-3]")| matches("^overall_engagement_[1-3]")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study"))
```
Engagement ($a$ = `r paste(round(engagement_alpha$raw_alpha, 2), sep = ", ")`)   

```{r include = render_html}
(ease_alpha = paste0("s", c(2:5)) %>% 
  # list(s2, s3, s4, s5) %>% 
       mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, matches("^ease_[1-2|4]")| matches("^overall_ease_[1|3|5]")) %>% 
  map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "Study"))
```
Ease ($a$ = `r paste(round(ease_alpha$raw_alpha, 2), sep = ", ")`)   


See Table \@ref(tab:scale-descriptives) for descriptive statisitcs of key variables. 
```{r scale-descriptives}
objects(pattern = "_alpha$") %>%
  mget(envir = .GlobalEnv, mode = "list") %>% 
  map_dfr(dplyr::select, Study, mean, sd, raw_alpha, .id = "outcome") %>% 
  mutate_if(is.double, ~sprintf("%.2f", .)) %>% 
  mutate(desc_stat = glue::glue("$M$ = {mean} ($SD$ = {sd}); $a$ = {raw_alpha}"),
         outcome = str_remove_all(outcome, "_alpha$")) %>% 
  dplyr::select(outcome, Study, desc_stat) %>% 
  pivot_wider(id_cols = outcome,
              names_from = Study, 
              # names_glue = "Study {.name}",
              values_from = desc_stat) %>% 
  dplyr::select(outcome, paste0("s", 1:5)) %>% 
  knitr::kable(caption = "Descriptive statistics of key variables")
```


The bivariate correlations between key measures in Study 1 \@ref(tab:bivariate-correlations-s1)  
```{r bivariate-correlations-s1}
s1 %>% 
  filter(exclusion == "eligible") %>% 
  select(promotion, prevention, ods) %>% 
  cor_keyvars() %>% 
  knitr::kable(caption = "Bivariate Correlations Between Key Measures in Study 1.")
```

in Studies 2 and 3, and
```{r results='asis'}
objects(pattern = "^s[2-3]") %>% 
  mget(envir = .GlobalEnv, mode = "list") %>% 
  map(filter, exclusion == "eligible") %>% 
  map(select, promotion, prevention, engage, ease) %>% 
  map(cor_keyvars) %>% 
  map(knitr::kable)
```

in Study 4 \@ref(tab:bivariate-correlations-s4).   
```{r bivariate-correlations-s4}
s4 %>% 
  filter(exclusion == "eligible") %>% 
  select(promotion, prevention, engage, ease, ods) %>% 
  cor_keyvars() %>% 
  knitr::kable(caption = "Bivariate Correlations Between Key Measures in Study 4.")
```

### Analytic Strategy  

```{r regression_meta}
# regressing RFQ (promotion and prevention) on y 
regression_meta <- function(df, y) {
  lmfit <- df %>% 
    # filter(exclusion == "eligible") %>% # excluding ineligible participants
    centre_pred(var = c("promotion", "prevention")) %>% # centring predictors
    lm(eval(rlang::sym(y)) ~ promotion.c + prevention.c, # fit regression
       data = .)
  list(r2 = broom::glance(lmfit)$r.squared, # regression model R2
       promotion_t = broom::tidy(lmfit)$statistic[2], # t-value 
       prevention_t = broom::tidy(lmfit)$statistic[3],
       promotion_b = broom::tidy(lmfit)$estimate[2], # estimate
       prevention_b = broom::tidy(lmfit)$estimate[3],
       promotion_se = broom::tidy(lmfit)$std.error[2], # std. error
       prevention_se = broom::tidy(lmfit)$std.error[3],
       promotion_p = broom::tidy(lmfit)$p.value[2], # p-value
       prevention_p = broom::tidy(lmfit)$p.value[3]) 
}
```

```{r engage_stats, include = render_html}
# predictor: `engagement` with the same items across studies  
(engage_meta <- list(s2, s3, s4, s5) %>% 
   map(filter, exclusion == "eligible") %>% 
   map_dfr(regression_meta, y = "engage", .id = "Study") %>% 
   mutate(ni = n_1to5[-1],
          Study = 2:5))
```
```{r ease_stats, include = render_html}
(ease_meta <- list(s2, s3, s4, s5)  %>% 
  map(filter, exclusion == "eligible") %>% 
  map_dfr(regression_meta, y = "ease", .id = "Study") %>% 
   mutate(ni = n_1to5[-1],
          Study = 2:5))
```
```{r success_stats, include = render_html}
(success_meta <- list(s1, s4, s5) %>% 
   map(filter, exclusion == "eligible") %>% 
  map_dfr(regression_meta, y = "ods", .id = "Study") %>% 
   mutate(ni = n_1to5[c(1, 4, 5)],
          Study = c(1, 4, 5)))
```

```{r include = render_html}
# combination of outcome (engagement, ease, and success) and RFQ (promotion and prevention)
meta_dataset = list(meta_data = list(engage_meta, ease_meta, success_meta),
                    term = alist(promotion_t, prevention_t)) %>% 
  cross_df() %>% 
  as.list() 

rfq_outcome = apply(expand.grid(c("engage", "ease", "success"), c("prom", "prev")), 1, paste, collapse = "_")
```

```{r}
spcor = function(meta_data, term) {
  meta_data = meta_data %>%
    dplyr::select(ti = !!term,
                  r2i = r2,
                  ni = ni,
                  Study) %>% 
    mutate(mi = rep(3, nrow(.)))
  
  spcor_result  = metafor::escalc(data = meta_data,
                measure = "SPCOR", # semi-partial correlation
                ti = ti, 
                r2i = r2i,
                ni =  ni,
                mi = mi, # number of predictors
                slab = paste0(Study, " [N = ", ni, "]")) 
    
  return(spcor_result) 
}
```

See Table \@ref(tab:effect-size) for the individual effect size estimates from each study that were used in the meta-analyses.   
```{r effect-size}
meta_dataset %>% 
  purrr::pmap_dfr(.f = spcor, .id = "outcome_rfq") %>% 
  tibble() %>% 
  mutate(outcome_rfq = rep(rfq_outcome, c(4, 4, 3, 4, 4, 3))) %>% 
  # separate(outcome_rfq, into = c("rfq", "outcome"), sep = "_") %>% 
  dplyr::select(Study, outcome_rfq, yi) %>% 
  spread(outcome_rfq, yi) %>% 
   mutate_at(vars(-Study), ~sprintf("%.2f", .)) %>% 
  dplyr::select(Study, engage_prom, engage_prev, ease_prom, ease_prev, success_prom, success_prev) %>% 
  # dplyr::select(Study, starts_with("engage_"), starts_with("ease_"), starts_with("success_")) %>% 
  # papaja::apa_table(caption = "Effect Size Estimates in Semi-Partial Correlation Coefficients")
  knitr::kable(caption = "Effect Size Estimates in Semi-Partial Correlation Coefficients")
```



```{r heterogeneity}
q_stats = list(meta_data = list(engage_meta, ease_meta, success_meta), # data containing effect sizes
                    term = alist(promotion_t, prevention_t)) %>%  # predictors
  cross_df() %>% 
  as.list() %>% 
  purrr::pmap(.f = report_meta) %>% 
  map_dfr(broom::glance, .id = "model") %>% 
  mutate(model = c("engage_prom",  "ease_prom", "success_prom", "engage_prev", "ease_prev", "success_prev"),
         p.value.cochran.qe = ifelse(p.value.cochran.qe < 0.001, "< .001", 
                                     gsub("^0.", "= .", sprintf("%0.2f", p.value.cochran.qe))),
         cochran.qe = round(cochran.qe, 2),
         apa_report = glue::glue("$Q$({df.residual}) = {cochran.qe}, $p$ {p.value.cochran.qe}"))
```

engagement as an outcome and promotion, `r q_stats$apa_report[q_stats$model=="engage_prom"]`, and prevention, `r q_stats$apa_report[q_stats$model=="engage_prev"]`, focus as predictors.

ease as an outcome and promotion, `r q_stats$apa_report[q_stats$model=="ease_prom"]`, and prevention, `r q_stats$apa_report[q_stats$model=="ease_prev"]`, focus as predictors.

success as an outcome and promotion, `r q_stats$apa_report[q_stats$model=="success_prom"]`, and prevention, `r q_stats$apa_report[q_stats$model=="success_prev"]`, focus as predictors.

## Results and Discussion  

### Meta-Analyses of the Associations between Regulatory Focus and Online Dating Experience and Success

```{r meta_results, include = render_html}
meta_results = meta_dataset %>% 
  purrr::pmap(.f = report_meta) %>% 
  map_dfr(broom::tidy, .id = "model") %>% 
  mutate(model = rfq_outcome) %>% 
  separate(model, into = c("outcome", "rfq"), sep = "_") %>% 
  select(-term, -type)
```

```{r meta_engage, include = render_html}
meta_results %>% filter(outcome == "engage")
```

The first meta-analysis with engagement as an outcome revealed that the overall effects of promotion focus `r meta_summary(meta_results)[[1]]`, and prevention focus, `r meta_summary(meta_results)[[4]]` were positive and significant. 

```{r meta_ease, include = render_html}
meta_results %>% filter(outcome == "ease")
```
The second meta-analysis with ease as an outcome revealed that promotion focus had a significant positive association with ease, `r meta_summary(meta_results)[[2]]`, whereas prevention focus had a significant negative association, `r meta_summary(meta_results)[[5]]`, with ease of browsing online dating profiles.


```{r ease_reml, include = render_html}
(ease_reml = c("promotion_t", "prevention_t") %>% 
  map(report_meta, meta_data = ease_meta, method = "REML") %>% 
  map_dfr(broom::tidy, .id = "rfq") %>% 
  mutate(rfq = c("promotion", "prevention")))
```

A random effects test of the overall effects of promotion (`r meta_summary(ease_reml)[[1]]`) and prevention (`r meta_summary(ease_reml)[[2]]`) focus on ease were also significant and comparable to those of the fixed model. 

```{r meta_success, include = render_html}
meta_results %>% filter(outcome == "success")
```

Next, we examined the overall effects of promotion and prevention focus on perceived success in online dating. Whereas promotion focus was positively associated, `r meta_summary(meta_results)[[3]]`, prevention focus was negatively associated, `r meta_summary(meta_results)[[6]]`, with feeling generally successful using online dating. 


### Exploratory Mediation Analyses

```{r}
promotion_ods_model <- '
  # regressions
  ods ~ b1*engage + b2*ease + c1*promotion + prevention

  engage ~ a1*promotion + prevention
  ease ~ a2*promotion + prevention
  
  engage ~~ ease

  # indirect paths
  engage_indirect := a1 * b1
  ease_indirect := a2 * b2
  
  total_indirect := (a1 * b1) + (a2 * b2)
  
  # total
  direct := c1
  total := c1 + (a1 * b1) + (a2 * b2)
'
```

```{r cache = TRUE}
prom_mediation_raw = objects(pattern = "^s[4-5]$") %>% 
  mget(envir = .GlobalEnv) %>% 
  map(filter, exclusion == "eligible") %>% 
  map(~mutate_at(., vars(c("engage", "ease", "promotion", "prevention")), mean_x)) %>% 
  map(~sem(promotion_ods_model, 
           data = .x,
           se = "bootstrap",
           bootstrap = 5000)) 
```

```{r prom_mediation, cache = TRUE}
prom_mediation = prom_mediation_raw %>% 
  map_dfr(standardizedSolution, output = "pretty",
          .id = "study") %>% 
   mutate_at(c("est.std", "se", "z", "ci.lower", "ci.upper"), ~sprintf("%0.3f", .)) %>% 
   mutate(pvalue = ifelse(pvalue < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", pvalue))),
          apa_result = glue::glue("{est.std}, $SE$ = {se}, 95% CI [{ci.lower}, {ci.upper}], $z$ = {z}, $p$ {pvalue}"))
```

```{r include = render_html}
prom_mediation %>% 
  mutate(label = glue::glue("{lhs} {op} {rhs}"), 
      .after = study) %>% 
  dplyr::select(study, label, est.std:ci.upper)
```

  Using Study 4, we conducted two exploratory mediation analyses separately for promotion and prevention focus as predictors. The mediation analysis with promotion focus as a predictor revealed a significant indirect effect through engagement, $a_1b_1$ = `r prom_mediation$apa_result[prom_mediation$study == "s4" & prom_mediation$lhs == "engage_indirect"]`, but a nonsignificant effect through ease, $a2b2$ = `r prom_mediation$apa_result[prom_mediation$study=="s4" & prom_mediation$lhs == "ease_indirect"]`. The total effect of promotion focus on online dating success, c = `r prom_mediation$apa_result[prom_mediation$study=="s4" & prom_mediation$lhs == "total"]`, was no longer significant when the two indirect effects were taken into account, c’ = `r prom_mediation$apa_result[prom_mediation$study=="s4" & prom_mediation$lhs == "direct"]`.


```{r}
# with ease + engage as mediators (in light of the meta-analysis result excluding the follow-up)
prevention_ods_model <- '
  # regressions
  ods ~ b1*engage + b2*ease + c1*prevention + promotion

  engage ~ a1*prevention + promotion
  ease ~ a2*prevention + promotion
  
  engage ~~ ease

  # indirect paths
  engage_indirect := a1 * b1
  ease_indirect := a2 * b2
  
  total_indirect := (a1 * b1) + (a2 * b2)
  
  # total
  direct := c1
  total := c1 + (a1 * b1) + (a2 * b2)
'
```


```{r cache = TRUE}
prev_mediation_raw = objects(pattern = "^s[4-5]$") %>% 
   mget(envir = .GlobalEnv) %>% 
   map(filter, exclusion == "eligible") %>% 
   map(~mutate_at(., vars(c("engage", "ease", "prevention", "promotion")), mean_x)) %>% 
   map(~sem(prevention_ods_model, 
            data = .x,
            se = "bootstrap",
            bootstrap = 5000)) 

```

```{r prev_medation, cache = TRUE}
prev_mediation = prev_mediation_raw %>% 
   map_dfr(standardizedSolution, 
           output = "pretty",
           .id = "study") %>% 
   mutate_at(c("est.std", "se", "z", "ci.lower", "ci.upper"), ~sprintf("%0.3f", .)) %>% 
   mutate(pvalue = ifelse(pvalue < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", pvalue))),
          apa_result = glue::glue("{est.std}, $SE$ = {se}, 95% CI [{ci.lower}, {ci.upper}], $z$ = {z}, $p$ {pvalue}"))
```

```{r include = render_html}
prev_mediation %>% 
  mutate(label = glue::glue("{lhs} {op} {rhs}"), 
      .after = study) %>% 
  dplyr::select(study, label, est.std:ci.upper)
```

  We next examined whether the prevention focus is associated with online dating success indirectly through a difficult profile browsing experience. The analysis revealed nonsignificant indirect effects through engagement, $a_1b_1$ = `r prev_mediation$apa_result[prev_mediation$study=="s4" & prev_mediation$lhs == "engage_indirect"]`, and ease, $a_2b_2$ = `r prev_mediation$apa_result[prev_mediation$study=="s4" & prev_mediation$lhs == "ease_indirect"]`. The total effect of prevention focus on online dating success was significant, $c$ = `r prev_mediation$apa_result[prev_mediation$study=="s4" & prev_mediation$lhs == "total"]`, and remained significant when the indirect effects through online dating experience were taken into account, $c’$ = `r prev_mediation$apa_result[prev_mediation$study=="s4" & prev_mediation$lhs == "direct"]`.

# Study 5: Preregistered Replication  
## Method  
### Participants   

```{r include = render_html}
library(lubridate)

s5 %>% 
  mutate(duration = time_length(as.duration(StartDate %--% EndDate), unit = "minutes")) %>% 
  # mutate(duration = minute(seconds_to_period(EndDate - StartDate))) %>% 
  # group_by(exclusion) %>% 
  summarise_at("duration", list(mean_duration = mean, sd_duration = sd), na.rm = T) 
```

Of these `r length(s5$PROLIFIC_PID)` participants, `r length(which(s5$exclusion=="ineligible"))` participants were excluded from analyses based on three preregistered criteria: failing attention check, providing inconsistent responses, and/or taking less than 6 minutes to complete the 12-minute ($X_{duration}$ = 11.90 minutes, SD = `r 586/60` minutes) questionnaire. 

The final sample of `r length(which(s5$exclusion=="eligible"))` eligible participants with an average age of `r study_info$mean_age[study_info$Study == "s5"]`.  
```{r include = render_html}
study_info %>% 
  filter(Study == "s5")
```
were 79 female, 66 male, and 4 non-binary individuals.	
```{r include = render_html}
s5 %>% 
  filter(exclusion == "eligible") %>% 
  count(gender)
```

### Measures  
#### Social Motive Measures  
```{r include = render_html}
list(prevention_alpha, promotion_alpha) %>% 
  map_dfr(filter, Study == "s5", .id = "RFQ") %>% 
  mutate(RFQ = c("prevention", "promotion"))
```

```{r}
list(select(s5[s5$exclusion=="eligible", ], matches("^bis_[0-9]")), #bis
     select(s5[s5$exclusion=="eligible", ], matches("^bas\\w_[0-9]"))) %>%  # bas
    map(psych::alpha, check.keys = TRUE) %>% 
  map_dfr("total", .id = "bisbas") %>% 
  mutate_if(is.double, ~sprintf("%.3f", .)) %>% 
  mutate(bisbas = c("bis", "bas"),
         desc_stat = glue::glue("$M$ = {mean}, ($SD$ = {sd}); $a$ = {raw_alpha}")) %>% 
  select(bisbas, desc_stat) %>% 
  knitr::kable(caption = "Descriptive statistics of general approach-avoidance motivations")
```


```{r include = render_html}
s5 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(promotion, bas, prevention, bis) %>% 
  corrr::correlate()
```
```{r include = render_html}
(r_appavo = list(select(s5[s5$exclusion=="eligible", ], promotion, prevention), # prom & bas
     select(s5[s5$exclusion=="eligible", ], bas, bis)) %>%  # prev & bis
  pmap(cor.test) %>% 
  map_dfr(broom::tidy, .id = "app_avo") %>% 
  mutate(app_avo = c("prom_bas", "prev_bis"),
         p.value = sprintf("%.3f", p.value),
         estimate = round(estimate, 3),
         apa_report = glue::glue("$r$({parameter}) = {estimate}, $p$ = {p.value}")) %>% 
  dplyr::select(-method, -alternative))
```

Promotion focus was positively associated with BAS, `r r_appavo$apa_report[r_appavo$app_avo == "prom_bas"]`, and prevention focus was positively associated with BIS, `r r_appavo$apa_report[r_appavo$app_avo == "prev_bis"]`.

## Results and Discussion   
See Table \@ref(tab:bivariate-correlations-s5) for the bivariate correlations between key measures in Study 5.  
```{r bivariate-correlations-s5}
# correlation tables of key measures 
s5 %>% 
  filter(exclusion == "eligible") %>% 
  dplyr::select(prevention, promotion, 
                bis, bas, 
                engage, ease, ods) %>% 
  cor_keyvars() %>% 
  knitr::kable(caption = "Zero-order Correlations of Key Measures")
```

See Supplemental Materials for the bivariate correlations broken down by demographics information.  

### Replication of Meta-Analyzed Effects of Promotion and Prevention Focus  
#### Online Dating Experience. 

```{r s5_experience}
s5_experience_rfq = s5 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas")) %>% 
  lm(cbind(engage, ease) ~ promotion.c + prevention.c,
     data = .)
```


```{r include = render_html}
car::Anova(s5_experience_rfq, type = 3, digits = 4) %>% 
  summary(multivariate = T, univariate = F, "Pillai")
```

The analysis replicated our findings; both promotion, V = 0.064, F(2, 146) = 5.03, p = .0077,  and prevention focus, V = 0.087, F(2, 146) = 6.98, p = .0013, were significant predictors of engagement and ease of browsing profiles. 


```{r include = render_html}
(s5_exp_regressions = broom::tidy(s5_experience_rfq) %>% 
  mutate_at(vars(estimate:statistic), round, 3) %>%
  mutate(p.value = ifelse(p.value < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", p.value))),
         apa_report = glue::glue("$b$ = {estimate}, $SE$ = {std.error}, $t$(147) = {statistic}, $p$ {p.value}")))
```

  Consistent with the meta-analytic findings, engagement while browsing online dating profiles was positively predicted by promotion focus, `r s5_exp_regressions$apa_report[s5_exp_regressions$term == "promotion.c" & s5_exp_regressions$response=="engage"]`, but not predicted by prevention focus, `r s5_exp_regressions$apa_report[s5_exp_regressions$term == "prevention.c" & s5_exp_regressions$response=="engage"]`. Contrary to our predictions, promotion focus was not a significant predictor of ease while browsing dating profiles, `r s5_exp_regressions$apa_report[s5_exp_regressions$term == "promotion.c" & s5_exp_regressions$response=="ease"]`, although results were in the expected direction. As predicted, prevention focus negatively predicted ease of use, `r s5_exp_regressions$apa_report[s5_exp_regressions$term == "prevention.c" & s5_exp_regressions$response=="ease"]`. 
  
#### Online Dating Success.  
```{r}
s5_ods_rfq = s5 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention")) %>% 
  lm(ods ~ promotion.c + prevention.c , 
     data = .) 
```

```{r}
s5_ods_omnibus = car::Anova(s5_ods_rfq) %>% 
  broom::tidy() %>% 
  filter(term != "Residuals") %>% 
  mutate(p.value = ifelse(p.value < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", p.value))),
         statistic = sprintf("%.2f", statistic),
                apa_report = glue::glue("$F$({df}, 147) = {statistic}, $p$ {p.value}"))
```


A multiple linear regression analysis with online dating success and both promotion and prevention focus as predictors replicated the meta-analysis: There were significant main effects of promotion focus, `r s5_ods_omnibus$apa_report[s5_ods_omnibus$term =="promotion.c"]`, and prevention focus, `r s5_ods_omnibus$apa_report[s5_ods_omnibus$term =="prevention.c"]`. 

```{r}
(s5_ods_regressions = s5_ods_rfq %>% 
  broom::tidy() %>%
  mutate_at(vars(estimate:statistic), round, 3) %>%
  mutate(p.value = ifelse(p.value < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", p.value))),
         apa_report = glue::glue("$b$ = {estimate}, $SE$ = {std.error}, $t$(147) = {statistic}, $p$ {p.value}")))
```

The follow-up univariate analysis revealed that perceived success in online dating was positively predicted by promotion focus, `r s5_ods_regressions$apa_report[s5_ods_regressions$term =="promotion.c"]`, and negatively predicted by prevention focus, `r s5_ods_regressions$apa_report[s5_ods_regressions$term =="prevention.c"]`. 

### Exploratory Mediation Analysis  
```{r include = render_html}
prom_mediation %>% 
  filter(study == "s5")
```

  The mediation analysis with promotion focus as a predictor was consistent with our findings from Study 4. There was a significant indirect effect between promotion focus and perceived success through engagement, $a_1b_1$ = `r prom_mediation$apa_result[prom_mediation$study=="s5" & prom_mediation$lhs == "engage_indirect"]`, and a nonsignificant indirect effect through ease, $a_2b_2$ = `r prom_mediation$apa_result[prom_mediation$study=="s5" & prom_mediation$lhs == "ease_indirect"]`. We also found a significant total effect of promotion focus on perceived success, c = `r prom_mediation$apa_result[prom_mediation$study=="s5" & prom_mediation$lhs == "total"]`, which became nonsignificant when the indirect effects were taken into account, c’ = `r prom_mediation$apa_result[prom_mediation$study=="s5" & prom_mediation$lhs == "direct"]`. 

```{r include = render_html}
prev_mediation %>% 
  filter(study == "s5")
```

The mediation analysis result with prevention focus as a predictor was inconsistent with that of Study 4 that found no mediation effect through engagement or ease. Although the indirect effect through engagement was nonsignificant, $a_1b_1$ = `r prev_mediation$apa_result[prev_mediation$study== "s5" & prev_mediation$lhs == "engage_indirect"]`, which is consistent with Study 4; the indirect effect through ease, $a_2b_2$ = `r prev_mediation$apa_result[prev_mediation$study== "s5" & prev_mediation$lhs == "ease_indirect"]`, was significant in Study 5. The significant total effect of prevention focus on online dating success ($c$ = `r prev_mediation$apa_result[prev_mediation$study== "s5" & prev_mediation$lhs == "total"]`) was no longer significant $c’$ = `r prev_mediation$apa_result[prev_mediation$study== "s5" & prev_mediation$lhs == "direct"]` when the indirect effects were taken into account. 

### Social Motives in Online Dating

```{r include = render_html}
s5_experience_appavo = s5 %>% 
    filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas", 
                      "rfq_prom", "rfq_prev")) %>% 
  lm(cbind(engage, ease) ~ promotion.c + prevention.c + bis.c + bas.c,
     data = .)
```

```{r include = render_html}
car::Anova(s5_experience_appavo, type = 3) %>% 
  summary(multivariate = TRUE, "Pillai", digits = 3)
```

When all four measures of approach and avoidance motivation are entered simultaneously, profile-browsing experience as a whole was significantly predicted by promotion focus, $V$ = 0.048, $F$(2, 144) = 3.64, $p$ = .029,  and prevention focus, $V$ = 0.044, $F$(2, 144) = 3.33, $p$ = .039, but not by BAS, $V$ = 0.020, $F$(2, 144) = 1.48, $p$ = .23, or BIS, $V$ = 0.023, $F$(2, 144) = 1.70, $p$ = .19. 

```{r include = render_html}
(s5_exp_appavo_regressions = s5_experience_appavo %>% 
   broom::tidy() %>%
   mutate_at(vars(estimate:statistic), round, 3) %>%
   mutate(p.value = ifelse(p.value < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", p.value))),
          apa_report = glue::glue("$b$ = {estimate}, $SE$ = {std.error},
                                  $t$({s5_experience_appavo$df.residual}) = {statistic}, $p$ {p.value}")))
```

Univariate analyses revealed that engagement was significantly predicted by promotion focus, `r s5_exp_appavo_regressions$apa_report[s5_exp_appavo_regressions$term == "promotion.c" & s5_exp_appavo_regressions$response=="engage"]`, and ease was significantly predicted by prevention focus, `r s5_exp_appavo_regressions$apa_report[s5_exp_appavo_regressions$term == "prevention.c" & s5_exp_appavo_regressions$response=="ease"]`.


BIS and BAS were not significant predictors of engagement and ease (see Table \@ref(tab:uni-appavo) for the full model estimates), suggesting regulatory focus might be associated with online dating experience above and beyond general social motives. 

```{r}
s5_ods_appavo_lm = s5 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas")) %>% 
  lm(ods ~ promotion.c + prevention.c + bis.c + bas.c ,
     data = .) 

s5_ods_appavo = s5_ods_appavo_lm %>% 
   broom::tidy() %>%
   mutate_at(vars(estimate:statistic), round, 3) %>%
   mutate(p.value = ifelse(p.value < 0.001, "< .001", gsub("^0.", "= .", sprintf("%0.2f", p.value))),
          apa_report = glue::glue("$b$ = {estimate}, $SE$ = {std.error}, $t$({s5_ods_appavo_lm$df.residual}) = {statistic}, $p$ {p.value}"))
```

We then examined subjective success in online dating and its associations with approach and avoidance motivations. With BIS/BAS as covariates, promotion (`r s5_ods_appavo$apa_report[s5_ods_appavo$term == "promotion.c"]`) and prevention (`r s5_ods_appavo$apa_report[s5_ods_appavo$term == "prevention.c"]`) focus were no longer significant predictors of online dating success. In addition, neither BAS, `r s5_ods_appavo$apa_report[s5_ods_appavo$term == "bas.c"]`, nor BIS, `r s5_ods_appavo$apa_report[s5_ods_appavo$term == "bis.c"]`, was a significant predictor of online dating success.


```{r uni-appavo}
full_join(s5_exp_appavo_regressions, s5_ods_appavo) %>% 
  mutate(response = ifelse(is.na(response), "Online Dating Success", str_to_title(response))) %>% 
  mutate_at("p.value", ~str_remove_all(., paste(c("=" , "<"), collapse = "|"))) %>% 
  mutate_at("term", ~str_replace_all(., c("promotion.c" = "Promotion",
                                          "prevention.c" = "Prevention",
                                          "bis.c" = "BIS" ,
                                          "bas.c" = "BAS"))) %>% 
  rename(Outcome = "response",
    Variable = "term",
         SE = "std.error",
         `$t$(145)` = "statistic",
         p = "p.value") %>% 
  select(-apa_report) %>% 
  knitr::kable(caption = "Univariate Estimates of the Full Models for Approach and Avoidance Motivation Measures")
```

```{r include = render_html}
s5 %>% 
  filter(exclusion == "eligible") %>% 
  centre_pred(var = c("promotion", "prevention", 
                      "bis", "bas")) %>% 
  lm(ods ~ promotion.c + prevention.c + bis.c + bas.c ,
     data = .) %>% 
  sjPlot::tab_model(show.stat = TRUE, show.se = TRUE, show.std = "std", string.stat = "\bt",
                    dv.labels = "Online Dating Success")
```


# Supplemental Materials   
## Scale Validation  
```{r child="pr_supplemental_materials.Rmd"}
```

## Exploratory analyses   
```{r child="pr_r&r_supplemental_materials.Rmd"}
```
# References   
```{r}
# citing R and r-pacakges 
papaja::r_refs(file = "r-references.bib")
my_citations <- papaja::cite_r(file = "r-references.bib")
```

`r my_citations`

